---
title: "Final Project - Stat 123"
author: "Paxon Fischer"
date: "February 28, 2017"
output: word_document
classoption: landscape
---

```{r setup, include=FALSE, echo = FALSE}
require(knitr)
opts_knit$set(root.dir="C:/Users/paxon/Documents/data", echo = TRUE)
```

## R Markdown

This document represents a Student Report with 4 sections that compare overall scores and percentages as well as their respective domain percentages and socres. It also includes an Exam Report with 3 sections that compare difficulty of exam based on question number and exam form. 

```{r read in libtraries, echo = FALSE, warning = FALSE, message = FALSE}
library(plyr)
library(dplyr)

```

```{r readFormA, echo = FALSE}
#FORM A
FormA <- read.csv("FormA.csv", header = FALSE, stringsAsFactors = FALSE) 
DomainsA <- read.csv("Domains FormA.csv", stringsAsFactors = FALSE)
names(DomainsA)[4] <- c("Question")
names(DomainsA)[3] <- c("dnumber")
#Separate Answer Key from Form
FormAKey <- FormA[1,]
FormA <- FormA[-1,]

#Find Scores for each student
students <- numeric()
students_vert <- NULL
for (i in 1:50) {
  for (j in 2:151) {
    students <- as.numeric(FormA[i,j] == FormAKey[1,j])
    students_vert <- rbind(students_vert, c(FormA[i,1], j-1, students))
  }
}
colnames(students_vert) <- c("Student", "Question", "Score")
FormA.Domains <- cbind(students_vert, DomainsA[,-4])
FormA.Domains <- mutate(FormA.Domains, Form = "A")
```

```{r readFormB, echo = FALSE}
#FORM B
FormB <- read.csv("FormB.csv", header = FALSE, stringsAsFactors = FALSE) 
DomainsB <- read.csv("Domains FormB.csv", stringsAsFactors = FALSE)
names(DomainsB)[4] <- c("Question")
names(DomainsB)[3] <- c("dnumber")
#Separate Answer Key from Form
FormBKey <- FormB[1,]
FormB <- FormB[-1,]

#Find Scores for each student
students <- numeric()
students_vert <- NULL
for (i in 1:49) {
  for (j in 2:151) {
    students <- as.numeric(FormB[i,j] == FormBKey[1,j])
    students_vert <- rbind(students_vert, c(FormB[i,1], j-1, students))
  }
}
colnames(students_vert) <- c("Student", "Question", "Score")
FormB.Domains <- cbind(students_vert, DomainsB[,-4])
FormB.Domains <- mutate(FormB.Domains, Form = "B")
```

```{r readFormC, echo = FALSE}
#FORM C
FormC <- read.csv("FormC.csv", header = FALSE, stringsAsFactors = FALSE) 
DomainsC <- read.csv("Domains FormC.csv", stringsAsFactors = FALSE)
names(DomainsC)[4] <- c("Question")
names(DomainsC)[3] <- c("dnumber")
#Separate Answer Key from Form
FormCKey <- FormC[51,]
FormC <- FormC[-51,]

#Find Scores for each student
students <- numeric()
students_vert <- NULL
for (i in 1:50) {
  for (j in 2:151) {
    students <- as.numeric(FormC[i,j] == FormCKey[1,j])
    students_vert <- rbind(students_vert, c(FormC[i,1], j-1, students))
  }
}
colnames(students_vert) <- c("Student", "Question", "Score")
FormC.Domains <- cbind(students_vert, DomainsC[,-4])
FormC.Domains <- mutate(FormC.Domains, Form = "C")
```

```{r readFormD, echo = FALSE}
#FORM D
FormD <- read.csv("FormD.csv", header = FALSE, stringsAsFactors = FALSE) 
DomainsD <- read.csv("Domains FormD.csv", stringsAsFactors = FALSE)
names(DomainsD)[4] <- c("Question")
names(DomainsD)[3] <- c("dnumber")
#Separate Answer Key from Form
FormDKey <- FormD[25,]
FormD <- FormD[-25,]

#Find Scores for each student
students <- numeric()
students_vert <- NULL
for (i in 1:50) {
  for (j in 2:151) {
    students <- as.numeric(FormD[i,j] == FormDKey[1,j])
    students_vert <- rbind(students_vert, c(FormD[i,1], j-1, students))
  }
}
colnames(students_vert) <- c("Student", "Question", "Score")
FormD.Domains <- cbind(students_vert, DomainsD[,-4])
FormD.Domains <- mutate(FormD.Domains, Form = "D")
```

```{r Combine forms, echo = FALSE}
report <- rbind(FormA.Domains, FormB.Domains, FormC.Domains, FormD.Domains)
report$Score <- as.integer(as.character(report$Score))
report$Student <- as.integer(as.character(report$Student))
report$Question <- as.integer(as.character(report$Question))
```

```{r Find Overal Percentages and Scores along with their domains, echo = FALSE}
#Overall Percentages Separated by Form
OverallPercentageA <- aggregate(Score ~ Student, mean, data = report[report$Form == "A",])
OverallPercentageA$Form <- rep("A", length(OverallPercentageA$Student))
OverallPercentageB <- aggregate(Score ~ Student, mean, data = report[report$Form == "B",])
OverallPercentageB$Form <- rep("B", length(OverallPercentageB$Student))
OverallPercentageC <- aggregate(Score ~ Student, mean, data = report[report$Form == "C",])
OverallPercentageC$Form <- rep("C", length(OverallPercentageC$Student))
OverallPercentageD <- aggregate(Score ~ Student, mean, data = report[report$Form == "D",])
OverallPercentageD$Form <- rep("D", length(OverallPercentageD$Student))

#Bind togheter Overall Percentage Scores and reorder
OverallPercentage <- as.data.frame(rbind(OverallPercentageA, OverallPercentageB, OverallPercentageC, OverallPercentageD))
OverallPercentage <- OverallPercentage[order(OverallPercentage$Student),]
names(OverallPercentage)[3] <- c("Form") 
names(OverallPercentage)[2] <- c("Overall Percentage") 
OverallPercentage <- OverallPercentage[,c(1,3,2)]

#Overall Score Calculation
OverallScore <- aggregate(Score ~ Student, sum, data = report)
names(OverallScore)[2] <- c("Overall Score") 

#Domain Percentages
dp1 <- aggregate(Score ~ Student, mean, data = report[report$dnumber == 1,])
names(dp1)[2] <- c("Domain Percentage 1") 
dp2 <- aggregate(Score ~ Student, mean, data = report[report$dnumber == 2,])
names(dp2)[2] <- c("Domain Percentage 2") 
dp3 <- aggregate(Score ~ Student, mean, data = report[report$dnumber == 3,])
names(dp3)[2] <- c("Domain Percentage 3") 
dp4 <- aggregate(Score ~ Student, mean, data = report[report$dnumber == 4,])
names(dp4)[2] <- c("Domain Percentage 4") 
dp5 <- aggregate(Score ~ Student, mean, data = report[report$dnumber == 5,])
names(dp5)[2] <- c("Domain Percentage 5") 

#Domain Scores
ds1 <- aggregate(Score ~ Student, sum, data = report[report$dnumber == 1,])
names(ds1)[2] <- c("Domain Score 1") 
ds2 <- aggregate(Score ~ Student, sum, data = report[report$dnumber == 2,])
names(ds2)[2] <- c("Domain Score 2") 
ds3 <- aggregate(Score ~ Student, sum, data = report[report$dnumber == 3,])
names(ds3)[2] <- c("Domain Score 3") 
ds4 <- aggregate(Score ~ Student, sum, data = report[report$dnumber == 4,])
names(ds4)[2] <- c("Domain Score 4") 
ds5 <- aggregate(Score ~ Student, sum, data = report[report$dnumber == 5,])
names(ds5)[2] <- c("Domain Score 5") 
```

```{r Student Report Section 1, echo = FALSE}
studentreport1 <- cbind(OverallPercentage, OverallScore, ds1, ds2, ds3, ds4, ds5, dp1, dp2, dp3, dp4, dp5)
studentreport1 <- studentreport1[,-c(4,6,8,10,12,14,16,18,20,22,24)]
```

## Student Report
### Section 1

```{r Print Student Report Section 1}
studentreport1
```


```{r Student Report Section 2, echo = FALSE}
studentreport2 <- cbind(OverallScore, OverallPercentage, dp1, dp2, dp3, dp4, dp5, ds1, ds2, ds3, ds4, ds5)
studentreport2 <- studentreport2[,-c(3,6,8,10,12,14,16,18,20,22,24)]
studentreport2 <- studentreport2[,c(1,3,4,2,5:14)]
studentreport2 <- studentreport2[order(studentreport2$`Overall Percentage`),]
```

## Student Report
# Section 2

```{r Print Student Report Section 2}
studentreport2
```

## Student Report
### Section 3

```{r Student Report Section 3, echo = FALSE}
boxplot(studentreport1$`Domain Percentage 1`,
        studentreport1$`Domain Percentage 2`,
        studentreport1$`Domain Percentage 3`,
        studentreport1$`Domain Percentage 4`,
        studentreport1$`Domain Percentage 5`,
        col = c(2:6), main="Overall Percentage of each Domain", 
  	xlab="Domain Number", ylab="Percentage")
axis(1, at = c(1:5), labels = c("1", "2", "3", "4", "5"))
```

## Student Report
### Section 4

```{r Student Report Section 4, echo = FALSE}
boxplot(studentreport1$`Domain Percentage 1`[studentreport1$Form == "A"],
        studentreport1$`Domain Percentage 2`[studentreport1$Form == "A"],
        studentreport1$`Domain Percentage 3`[studentreport1$Form == "A"],
        studentreport1$`Domain Percentage 4`[studentreport1$Form == "A"],
        studentreport1$`Domain Percentage 5`[studentreport1$Form == "A"],
        studentreport1$`Domain Percentage 1`[studentreport1$Form == "B"],
        studentreport1$`Domain Percentage 2`[studentreport1$Form == "B"],
        studentreport1$`Domain Percentage 3`[studentreport1$Form == "B"],
        studentreport1$`Domain Percentage 4`[studentreport1$Form == "B"],
        studentreport1$`Domain Percentage 5`[studentreport1$Form == "B"],
        studentreport1$`Domain Percentage 1`[studentreport1$Form == "C"],
        studentreport1$`Domain Percentage 2`[studentreport1$Form == "C"],
        studentreport1$`Domain Percentage 3`[studentreport1$Form == "C"],
        studentreport1$`Domain Percentage 4`[studentreport1$Form == "C"],
        studentreport1$`Domain Percentage 5`[studentreport1$Form == "C"],
        studentreport1$`Domain Percentage 1`[studentreport1$Form == "D"],
        studentreport1$`Domain Percentage 2`[studentreport1$Form == "D"],
        studentreport1$`Domain Percentage 3`[studentreport1$Form == "D"],
        studentreport1$`Domain Percentage 4`[studentreport1$Form == "D"],
        studentreport1$`Domain Percentage 5`[studentreport1$Form == "D"],main="Domain Percentage of each Form", 
  	    xlab="Domain Number and Exam Form", ylab="Domain Percentage"
)
axis(1, at = c(1:20), labels = c("1A", "2A", "3A", "4A", "5A",
                                 "1B", "2B", "3B", "4B", "5B",
                                 "1C", "2C", "3C", "4C", "5C",
                                 "1D", "2D", "3D", "4D", "5D"),  cex.axis = .5)
```

```{r Exam Report Overall Percentages, echo = FALSE}
#Get Overall Percentages for each Form
ExamOP.A <- aggregate(Score ~ Question, mean, data = report[report$Form == "A",])
ExamOP.A$Form <- rep("A", length(ExamOP.A$Question))
ExamOP.B <- aggregate(Score ~ Question, mean, data = report[report$Form == "B",])
ExamOP.B$Form <- rep("B", length(ExamOP.B$Question))
ExamOP.C <- aggregate(Score ~ Question, mean, data = report[report$Form == "C",])
ExamOP.C$Form <- rep("C", length(ExamOP.C$Question))
ExamOP.D <- aggregate(Score ~ Question, mean, data = report[report$Form == "D",])
ExamOP.D$Form <- rep("D", length(ExamOP.D$Question))

#Combine Exam Overal Percentages into one data frame and sort
ExamOP <- as.data.frame(rbind(ExamOP.A, ExamOP.B, ExamOP.C, ExamOP.D))
```

```{r Exam Report Section 1, echo = FALSE}
ExamReport1 <- ExamOP[,c(3,1,2)]
names(ExamReport1)[3] <- c("Overall Percentage")
```

## Exam Report
### Section 1

```{r Print Exam Report Section 1}
ExamReport1
```

```{r Exam Report Section 2, echo = FALSE}
ExamReport2 <- ExamOP[order(ExamOP$Score),]
ExamReport2 <- ExamReport2[,c(2,3,1)]
names(ExamReport2)[1] <- c("Overall Percentage")
```

## Exam Report
### Section 2

```{r Print Exam Report Section 2}
ExamReport2
```

## Exam Report
### Section 3

```{r Exam Report Section 3, echo = FALSE}
boxplot(ExamReport1$`Overall Percentage`[ExamReport1$Form == "A"],
        ExamReport1$`Overall Percentage`[ExamReport1$Form == "B"],
        ExamReport1$`Overall Percentage`[ExamReport1$Form == "C"],
        ExamReport1$`Overall Percentage`[ExamReport1$Form == "D"],
        col = c(2:6), main="Overall Percentage of each Form", 
  	xlab="Exam Form", ylab="Overall Percentage")
axis(1, at = c(1,2,3,4), labels = c("A", "B", "C", "D"))
```
